---
title: "ComputationalRepro21_VilcekHW"
author: "Fred LaPolla"
date: "11/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework

1) Please explain 1 of Wilson et. al's suggestions for good practices in computational reproducibility:


Place a brief explanatory comment at the start of every program
I think it is extremely important to annotate and comment out your codde as this will make it easier for others to replicate in the long run. Often styles of coding vary drastically so it is important to annotate to an extent where almost any user understands why something is written and how to use it. Whena. program can be run by multiple users as such this will make it more reproducible. 



2) Please find the square root of 4 to the 13th power, writing your code in the gray box below so that it executes and provides the answer. Hit the play button to make sure it works:

```{r}
newval <- sqrt(4^13)
newval
```

3) Save your file and add it to your GitHub repository at: https://classroom.github.com/a/WO52_vGE
